---
title: Home Work 3 (Case Study 1) – Collecting, Manipulating and Blending Data from
  Twitter
author: "DS501 - Introduction to Data Science"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

## Introduction

-   Go to <https://dev.twitter.com/apps/new> and log in, if necessary
-   Enter your Application Name, Description and your website address.
-   Set the callback URL <http://127.0.0.1:1410>
-   Accept the TOS, and solve the CAPTCHA.
-   Submit the form by clicking the Create your Twitter Application
-   Copy the consumer key (API key) and consumer secret from the screen into your application
-   Download twitter package from <https://github.com/geoffjentry/twitteR>

## Problem 1: Sampling Twitter Data with Streaming API about a certain topic

-   Select a topic that you are interested in, for example, "#WPI" or "#DataScience"
-   Use Twitter Streaming API to sample a collection of tweets about this topic in real time. (It would be recommended that the number of tweets should be larger than 50, but smaller than 500.
-   Store the tweets you downloaded into a local file (csv file)

```{r}
consumerKey = "FS8KA9WE0FbnWDODHbf4zyc3u"
consumerSecret = "Nrl4cyaJWSNWR2XnGxOF2tkUoNN8fmDgs1xkdGK54VLkJo3QGo"
accessToken = "905838785778380801-YcSvHOOS5hjhFRN9VA4BRIzcJnLA0Sw"
accessTokenSecret = "XTEdD7fUELBA8b7bYeTLzpWyUPZPaiqErvP7IFYkuQhB6"
```

```{r}
library(twitteR)
library(stringr)
setup_twitter_oauth(consumerKey, consumerSecret, accessToken, accessTokenSecret)
tweets = searchTwitter('#elonmusk', n=500)
tweets_df = twListToDF(tweets)
```

Report some statistics about the tweets you collected

-   The topic of interest: <elonmusk>
-   The total number of tweets collected: \< 500 \>

## Problem 2: Analyzing Tweets and Tweet Entities with Frequency Analysis

**1. Word Count:**

-   Use the tweets you collected in Problem 1, and compute the frequencies of the words being used in these tweets.

```{r}
# Your R code here
  install.packages("tidytext")
  install.packages("dplyr")
  
  library(tidytext)
  library(dplyr)
  
  write.csv(tweets_df, file = "tweets.csv", row.names = FALSE)
  
  #reading from the csv file
  tweet1<- read.csv("tweets.csv")
  
  #separating each word in the tweet
  tweets_words <- tweet1 %>%
  unnest_tokens(word,text)
  
  #adding new stop words 
  my_stop_words <- data.frame(word = c("rt","https","t.co"), lexicon = "my_stop_words")
  
  #appending added stop words with the original list
  stop_words <- bind_rows(stop_words,my_stop_words)
  
  #storing the words left after removing the stop words and sorting them
  top_freq <-tweets_words %>%
    anti_join(stop_words,by = "word") %>%
    count(word, sort = TRUE) 
```

-   Display a table of the top 30 words (ONLY) with their counts

```{r paged.print=FALSE}

#printing the top 30 stop words
  top_thirty <- top_freq %>%
    head(30)

  top_thirty
```

**2. Find the most popular tweets in your collection of tweets**

-   Please display a table of the top 10 tweets (ONLY) that are the most popular among your collection, i.e., the tweets with the largest number of retweet counts.

```{r}
    #View(tweetsDF)
    sort_tweets <- tweets[order(-tweet1$retweetCount)]
    top_ten <- head(sort_tweets,10)
    top_ten
```

**3. Find the most popular Tweet Entities in your collection of tweets**

Please display a table of the top 10 hashtags (ONLY), top 10 user mentions (ONLY) that are the most popular in your collection of tweets.

```{r}
# Your R code here
  install.packages("tidyverse")
  library(tidyverse)
  #selecting all the words that have # at their start
  hashtags <- tweet1 %>%
  mutate(hashtag = str_extract_all(text, "#\\S+")) %>%
  select(hashtag) %>%
  unnest()
  
  #counting the number of times each hashtag is used and sorting it.
  hashtag_counts <- hashtags %>%
    count(hashtag,sort = TRUE)

  #storing the top 10 hashtags
  top_hashtags <- hashtag_counts %>%
    head(10)
  
  #selecing all the words that have @ at their start
  mentions <-tweet1%>%
    mutate(mentions = str_extract_all(text, "@\\S+")) %>%
    select(mentions) %>%
    unnest()
  
  #counting the number of times each mention is used and sorting it
  mentions_counts <- mentions %>%
    count(mentions,sort = TRUE)
  
  #storing the top 10 mentions
  top_mentions <- mentions_counts %>%
    head(10)
  
  #printing top 10 hashtags
  top_hashtags
 
```

```{r}
#printing top 10 mentions
 top_mentions
```

## Problem 3: Getting any 20 friends and any 20 followers of a popular user in twitter

-   Choose a twitter user who has many followers, such as @hadleywickham.
-   Get the list of friends and followers of the twitter user.
-   Display 20 out of the followers, Display their ID numbers and screen names in a table.
-   Display 20 out of the friends (if the user has more than 20 friends), Display their ID numbers and screen names in a table.
-   Compute the mutual friends within the two groups, i.e., the users who are in both friend list and follower list, Display their ID numbers and screen names in a table

## Problem 4 (Optional): Explore the data

Run some additional experiments with your data to gain familiarity with the twitter data and twitter API \`\`

```{r paged.print=FALSE}
install.packages("sentimentr")
library(sentimentr)
tweet <- tweet1$text
sentiment_scores <- sentiment_by(tweet)
sentiment_scores
summary(sentiment_scores$ave_sentiment)


```

```{r}
summary(sentiment_scores$ave_sentiment)


```

In the summary most of the mean of the tweets is neutral, the maximum value is 0.8 which is also very close to neutral and minimum value which is -0.73.

```{r}
library(ggplot2)
qplot(sentiment_scores$ave_sentiment,   geom="histogram",binwidth=0.1,main="Review Sentiment Histogram")

```

The Y axis of the graph is the count or the number of tweets and the X axis is the sentiment score.

Seeing this distribution we can say that majority of the tweets have been neutral followed by positive tweets and the number of negative tweets being the least.

## Done

All set!

```{r}

```

**What do you need to submit?**

Report: please prepare a document, preferably using RMarkdown (less than 10 pages) to report what you found in the data.

-   **What data you collected?**

    I collected the data from #elonmusk and generated 500 tweets from this topic.

-   **Why this topic is interesting or important to you? (Motivations)**

    Considering the recent layoffs and the controversies Elon Musk gets himself into, I thought it would help me find interesting mentions and hashtags as well as an interesting histogram when sentiment analysis is done.

-   **How did you analyze the data?**

    I used libraries such as twitteR, stringR, dplyr, tidyverse and sentimentr in the case study.

    -   In the first problem, I used dplyr and tidytext.

    -   I used the functions write.csv to generate a csv from the List created by twitterAPI. I used unnest tokens to separate the words in the text column of the csv which included the tweets and removed the stop words from it. I created a new column "word" in which the remaining words were stored. Used the count function to sort the words and print the top 30.

    -   In my second problem, I used tidyverse.

    -   I created to "hashtags" and "mentions" dataframes which extracted all the words with \# and \@ in them and counted them. After which I printed the top ten in both parameters.

    -   Third problem was skipped.

    -   Upon doing prior research, third problem could have been easily solved using the rtweet library. There are functions such as get_followers() and lookup_users which can fetch the data in just a couple of lines of code.

    -   My initial idea for problem 3 was to identify the common topics between the mutual followers and printing an histogram of the most common topics.

    -   In fourth problem, I used sentimentr.

    -   The reason I picked #elonmusk was generate a variety of sentiments considering all the controversies he has been. I also generated a histogram to display the distribution of those sentiments.

-   **What did you find in the data? (please include figures or tables in the report)**

    -   The tables and histograms have already been included above in the document.

    -   The most frequent words include elonmusk himself, some nft companies, some crypto currencies as well as his products and some words in other languages.

    -   The most popular tweets seem to be bitcoin scams which is very alarming as twitter has been very strict with fishy or controversial tweets.

    -   Similarly, with the hashtags and mentions, most of them are crypto and nft companies and some words in other languages that I have very little idea about. It shows how diverse the audience of elon musk is which should have been obvious considering how large of a following he has .

    -   I also find out that the average sentiment in the tweets seem to be neutral with the mean being 0.06 with a distribution of more positive tweets compared with negative ones.

    -   I think, if were able to take a larger number of tweets, the distribution would have varied largely if the data received would have been through the timeline.

    -   If done so, there would have the high frequency words would have been the work Elon Musk has actually done instead of the random scam tweets that have been using #elonmusk to bait innocent people.

Please create an R Markdown PDF including the R code in a report format.

How to submit: - Submit on Course Webpage on Canvas as a PDF file ONLY. Do not email it to me.
